Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2015-01-29 paper.tex
modify algorithm and proof

\usepackage{cite}
\usepackage{amsmath}

@@

\begin{equation}
Minimize \max_{m \in M} \frac{U_{r,m,G^*}} {min_{r'} U_{r', m, G}}
\end{equation}

\begin{equation}
    G^* = (V,E^*), E^* \subset E
\end{equation}

\begin{equation}
    \begin{split}
    \forall (\epsilon, \gamma) \in \{ (E, r'), (E^*, r)\} \\
    \sum_{(i,j) \in \epsilon}f_{ab}(i,j)O_{(i,j)}^i - \sum_{(i,j) \in \epsilon}f_{ab}(i,j)I_{(i,j)}^i = \\
    \left\{
        \begin{array}{c}
        1, i = b \\
        -1, i = a \\
        0, i \neq a,b \\
        \end{array}
    \right.
    , \ \ \ \ a,b,i \in V, a \neq b, f_{ab}(i,j) \in \gamma
    \end{split}
\end{equation}

@@

@@

\section{Algorithm}
In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
should be put to sleep from the origin topology based on extended robust link utilization or algebraic connectivity, 
then compute the robust routing by demand-oblivious routing algorithm. There are two metrics
for selecting removed links, our two-phase algorithm is flexible because we can replace the metric with whatever
metric.

\subsection{Algebraic Connectivity}
Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
and $E$ is the set of links. We say $A(G)$ is the Adjacency Matrix of graph $G$, that include information for which
vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
$N = |V|$ and non-diagonal entry $a_{ij}$ equal to the number of edges from vertex $i$ to vertex $j$, in this paper,
$a_{ij}$ always be 1 if $(i,j) \in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.

We say $D(G)$ is the Degree Matrix of graph $G$, which is a diagonal matrix and diagonal entry $d_{ii}$ denote 
the degree of node $i$. It is obvious that there is $d_{ii} == \sum_{j} a_{ij}$.

Then we define Laplacian Matrix $L(G)$ of graph $G$ as the difference between Degree Matrix and Adjacency Matrix :
\begin{equation}
	L(G) = D(G) - A(G)
\end{equation}
where $D(G)$ is the Degree Matrix and $A(G)$ is the Adjacency Matrix.

In the mathematical field of graph theory, the number of eigenvalues equal to 0 is the number of connected 
componements of $G$, so the smallest eigenvalue always be 0 in arbitrary graph . And we call the second smallest one as
algebraic connectivity, which is greater than 0 if and only if graph $G$ is connected. Further more,  
it measures the connectivity and stability of graph, the greater of the value, the more connective of graph;
and it is a metric of average distance between any two vertices of graph $G$. We call the algebraic connectivity as
$\lambda_2(G)$.

Topology always have different algebraic connectivity values, it is clear that when one link is added or 
removed from the graph, the algebraic connectivity value changes accordingly. And we say the changed value
is the impact of this link on the graph. Supposed we sleep link $l$ from graph $G$, new graph is described as $G^*$, 
we defined the impact of link $l$ as :
\begin{equation}
	\Delta_l = \lambda_2(G) - \lambda_2(G^*)
\end{equation}
where $\lambda_2(G)$ and $\lambda_2(G^*)$ is algebraic connectivity of $G$ and $G^*$ respectly.

Clearly, $\Delta_l$ is always greater than 0, because graph will always lose connectivity when link is removed.
Further more, some link will play a more important role in the connectivity of graph, such as the backbone link 
of network topology. And we say a link $l$ affect more if $\Delta_l$ is greater.

\subsection{Extended Robust Link Utilization}
The demand-oblivious routing is not always the best one for 
specific $TM$, but good enough for a range of $TM$. we mentioned the definition of link utilization above when 
demand and routing are determined, as demand become oblivious, the definition is also not suitable. So we define
a notation named extended robust link utilization (ERLU) replace the normal link utilization like :
\begin{equation}
	u^e_{ij} = \frac {\sum_{a,b}f_{ab}(i,j)} {cap_{ij}}
\end{equation}

Proposing this definition for two consideration: firstly, the more flows across the link, the greater the $u^e_{ij}$ is;
secondly, the more fraction of one flow across the link, the greater the $u^e_{ij}$ is. The link with greater
ERLU is also more important than others in a sense. Although there is no demand here, we mean
there is more probability that this link have greater link utilization when specific demand come. Similarly, we define 
the impact of link $l$ as :
\begin{equation}
    \Delta_l = u^e_{l}
\end{equation}

And there is the same conclusion that a link $l$ affect more if $\Delta_l$ is greater.

\subsection{Algorithm Phase One}
REAR sleep as many links as possible without losing much connectivity or transportation of graph for different metrics. 
Originly,  we should calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.

For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
from small to big, output ordered list denoted as $\Gamma$: 
\begin{equation}
	\Gamma = \{..., l_i, ..., l_j, ...\}
\end{equation}
where $\Delta_{l_i} < \Delta_{l_j}$.

Pay attention we only compute the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
the order of `importance' among links in the graph.

Now we begin selecting which links should be sleep.
We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set 
$S = \emptyset$, and repeat our selecting process, each iteration we select one link, remove it from $\Gamma$ and put it into $S$. 
In iteration $i$, algorithm scan links as the order in $\Gamma$, we try to
remove this link from the graph to check if the graph is still connected and the energy conservation have not arrive the threshold.
If so, we select this one then go next iteration.
Otherwise choose the next link from $\Gamma$ for trying to remove. Algorithm
stop until all the links in $\Gamma$ is tried but no one is satisfied with both connectivity and power threhold.

So before going ahead our algorithm, there is another thing we should done, how to measure the power of graph.
We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{2}, and defined the difference of power consumption 
between two graphs as:
\begin{equation}
	diff_p = \frac{\rho(G_{S, l}^o)} {\rho(G^o)} * 100
\end{equation}
where $\rho(G_{S, l}^o)$ is the power consumption of the final graph, when the links set $S$ and 
link $l$ are both removed from the origin graph $G^o$, and the $\rho(G^o)$ is the power consumption of 
the origin graph.

If we set $diff_p$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
of this phase protect as much connectivity and transportation as possible. Following is our implementation:

\begin{table}[!th]
\begin{tabular}{ll}
\hline
\textbf{Algorithm REAR : Phase One}\\
\hline
$\:\:$\textbf{Input:} $G(V, E)$, $threhold$;\\
$\:\:$\textbf{Output:} $S$ in which links should be switched off;\\
$\quad\qquad\quad$ $G(V, E-S)$ which is the final network topology;\\
$\:\:$1:\ \textbf{for} {each link $l$ in $E$}\\
$\:\:$2:\quad\ $G^* \leftarrow G(V, E-\{l\})$;\\
$\:\:$3:\quad\ $\Gamma[l] \leftarrow \Delta_l \leftarrow \lambda_2(G) - \lambda_2(G^*)$;\\
$\:\:$4:\ Resort $\Gamma$ in increasing order based on $\Delta_l$;\\
$\:\:$5:\ $S \leftarrow \emptyset$, $goon \leftarrow true$;\\
$\:\:$6:\ \textbf{while} {$goon$}\\
$\:\:$7:\quad\  $goon \leftarrow false$;\\
$\:\:$8:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
$\:\:$9:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)>threhold$\\
$\:\:$10:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
$\:\:$11:\quad\ \quad\ \quad\ $goon \leftarrow true$;\\
$\:\:$12:\quad\ \quad\ \quad\ \textbf{break};\\
$\:\:$13:\ \textbf{return} $S, G(V, E-S)$;\\
\hline
\end{tabular}
\end{table}

\subsection{Algorihtm Phase Two}
Once we get the output network topology from the first phase based on either metric, it is time to compute
the robust routing. On one hand, computation process may cost too much time if we directly calculate the robust routing in 
the final graph; on the other hand, the robust routing based on the final graph may not be the best one.
There is a heuristic algorithm
based on the demand-oblivious routing on the origin graph, which should be obtained at first.
then adjust routing in details according to the links we switched off.

@@

\section{Samples and Proof}
For showing obilious performance ratio with energy constraint really make a difference in the switching off link 
process, we will explain it in two simple topologies, cliques and cycles. On the other hand, we also say that
there will be an upper bound for obilious performance ratio with energy constraint, and get the bound according
to the topology. For simpleness, we refer the energy constraint to the quantity of removed links.

@@

\subsection{Circles}
Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 1 show the six
nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$ in the figure.
Now suppose a traffic in the topology then calculate the optimal routing for it,
let $D_a$ and $C_a$ be the demand and capacity of the link, without loss of generality, we say the link $d$ is the 
bottleneck, i.e. with the maximum link utilization. There are two solutions for us, switching off the link $d$,
or the other link, such as link $f$.

For case one, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
is that all the traffic on the link $d$ will be put to the other path : $D \leftarrow C \leftarrow B \leftarrow A \leftarrow 
F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, according to our definition of
extended robust link utilization:

@@

so we have the extended robust link utilization in case one :

@@

For case two, similar to case one, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In sub 
case one:

@@

Because the link utilization of link $d$ is the maximum one in origin topology, we have as:

@@

So we get the extended robust link utilization in this case :
\begin{equation}
    (1 + \frac{D_f}{D_d}) < \frac{C_d}{C_f} + 1
\end{equation}

In sub case two, we get the new extended robust link utilization in link $E$:

@@

So we get the extended robust link utilization:

@@

\begin{equation}
    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\}
\end{equation}

Particularly, if all the links have the same capacity, the upper bound equal to 2 when switch off one link. Otherwise, the 
upper bound only dependent to the greatest ratio of link capacity.

\subsection{Cliques}
In clique topology, all the nodes connect to each other, it means that situation become more difficult because the traffic
can be adjusted to multi paths rather than one path in circle. And we will see that splitting traffic on multi paths is 
always better than put all the traffic to one, so if we get the upper bound of the worst case, it must be the upper bound
of other case. Similarly to circle topology, we say the link $a$ is the bottleneck, and we will switch off it or other link
like $b$.

In case one, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
traffic on link $a$. Otherwise if the link $b$ is the bottleneck, but we adjust the traffic on other links, it means that
we can do the same thing in the origin topology, and the bottleneck become link $b$ rather than $a$. It is conflict with our
assumption. So we have the extended robust link utilization as :

@@

In case two, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
the extended robust link utilization equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the
extended robust link utilization:

@@

If the bottleneck become new link $c$, similar to our proof of circle topology, we can get extended robust link utilization:
\begin{equation}
    \frac{\frac{D_c + D_b}{C_c}}{\frac{D_a}{C_a}} = \frac{D_c * C_a}{D_a * C_c} + \frac{D_b * C_a}{D_a * C_c} < 1 + \frac{C_b}{C_c}
\end{equation}

So we obtain the same conclusion as circle topology, the extended robust link utilization must be :

\begin{equation}
    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\}
\end{equation}

\subsection{Other Topology}
We can also see that, when we switch off different link, it really matters the performance which dependent on not only the 
demand or traffic, but also the capacity of links. Particularly, the upper bound is just related with the capacity of links.
And from our proof process, there is no special limitation for specific topology, so we can get the similar conclusion 
on other topology.

@@

When we switch off links, the topology lose connectivity and some routing paths will be failed, traffic on those paths will be 
adjusted to others, which result in the value of OPRE increased. We take margin from 1.5 to 3.5 and observe this phenomena from Figure.
Pay attention that we scale the y-axis as logarithm for comparing TMP and ERLU in one figure. Intuitively, we can see ERLU is always
better than TMP whatever margin or power saving target is, because ERLU consider much more than TMP, such as capacity and robust traffic 
flows. Another information from Figure 4 is that, we should carefully set the value of power saving for avoiding removing too much
links, which result in the OPRE increases rapidly, induce network congestions easily and make the robust routing be less `robust'.

@@

Comparing TMP and ERLU, the conclusion is similar to Figure 3, the latter is always better than the former. Even in some 
time, ERLU obtains more power saving but with a lower OPRE.

@@

We can observe that, ERLU is always shorter than TMP, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
equal to 1.5. And in the first removed links, the path stretching ratio is near 20\%.

@@

\bibitem{networking:gravity}
M.Roughan, A.Greenberg, C.Kalmanek, M.Rumsewicz, J.Yates, and Y.Zhang. Experience in measuring backbone traffic variability: models, metrics, measurements, and meaning. InProceedings of the 2nd Internet Measurement Workshop. ACM, 2002
\end{thebibliography}

>>>>

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

@@

\begin{center}
Minimize \quad $P^*(\{r\},M,G)$
\end{center}

\begin{center}
s.t. (1),\ (4)
\end{center}

\begin{center}
    $\forall a,b,i \in V$: \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad 
    \vspace{-0.3in}
\end{center}

\begin{equation}
    \begin{split}
    \sum_{j, s.t.(i,j) \in E}\hspace{-0.2in}f'_{ab}(i,j) - \hspace{-0.2in}\sum_{j, s.t.(j,i) \in E}\hspace{-0.2in}f'_{ab}(j,i) = 
    \left\{
        \begin{array}{c}
        \ \ 1, \ i = b \\
        -1, \ i = a \\
        \ \ \ \ \ 0, \ i \neq a,b \\
        \end{array}
    \right.
    \end{split}
\end{equation}

\begin{center}
    \vspace{0.1in}
    $\forall a,b,i \in V$: \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad
    \vspace{-0.3in}
\end{center}

\begin{equation}
    \begin{split}
    \sum_{j, s.t.(i,j) \in E^*}\hspace{-0.2in}f_{ab}(i,j) - \hspace{-0.3in}\sum_{j, s.t.(j,i) \in E^*}\hspace{-0.2in}f_{ab}(j,i) = 
    \left\{
        \begin{array}{c}
        \ \ 1, \ i = b \\
        -1, \ i = a \\
        \ \ \ \ \ 0, \ i \neq a,b \\
        \end{array}
    \right.
    \end{split}
\end{equation}

@@

\begin{equation}
    0 \leq f_{ab}(i,j),f'_{ab}(i,j) \leq 1
\end{equation}

@@

\section{Algorithm}
In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
should be put to sleep from the origin topology based on extended robust link utilization (ERLU), 
then compute the robust routing based on demand-oblivious routing algorithm.

\subsection{Extended Robust Link Utilization}
The demand-oblivious routing is not always the best one for specific $TM$, but good enough for a range of $TM$. 
we mentioned the definition of link utilization above when demand and routing are determined, as demand become 
oblivious, the definition is also not suitable. So we define a notation named extended robust link utilization (ERLU) 
replace the normal link utilization like :

\begin{equation}
	u^e_{ij} = \frac {\sum_{a,b}f_{ab}(i,j)} {cap_{ij}}
\end{equation}

Proposing this definition for two consideration: firstly, the more flows across the link, the greater the $u^e_{ij}$ is;
secondly, the more fraction of one flow across the link, the greater the $u^e_{ij}$ is. The link with greater
ERLU is also more important than others in a sense. Although there is no demand here, we mean
there is more probability that this link have greater link utilization when specific demand come.

\subsection{Algorithm Phase One}
REAR sleep as many links as possible without losing connectivity of graph. 
Originly,  we should calculate ERLU of all the links and sleep the lowest one from the graph, then repeat calculate and remove
process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.

For the origin graph, we calculate the ERLU of every link, and then sort these values
from small to big, output ordered list denoted as $\Gamma$: 
\begin{equation}
	\Gamma = \{..., l_i, ..., l_j, ...\}
\end{equation}
where $u^e_{l_i} < u^e_{l_j}$.

Pay attention we only compute the ERLU once at the begining of algorihtm, and the ordered list $\Gamma$ show 
the order of `importance' among links in the graph.

Now we begin selecting which link should be sleep.
We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set 
$S = \emptyset$, and repeat our selecting process, each iteration we select one link, remove it from $\Gamma$ and put it into $S$. 
In iteration $i$, algorithm scan links as the order in $\Gamma$, we try to
remove this link from the graph to check if the graph is still connected and the energy conservation have not arrive the threshold.
If so, we select it then go next iteration.
Otherwise choose the next link from $\Gamma$ for trying to remove. Algorithm
stop until all the links in $\Gamma$ is tried but no one is satisfied with both connectivity and power threhold.

But before going ahead our algorithm, there is another thing we should care, how to measure the power of graph.
We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{2}, and defined the difference of power consumption 
between two graphs as:
\begin{equation}
	diff_p = 1 - \theta = \frac{\rho(G_{S, l}^o)} {\rho(G^o)} * 100
\end{equation}
where $\rho(G_{S, l}^o)$ is the power consumption of the final graph, when the links set $S$ and 
link $l$ are both removed from the origin graph $G^o$, and the $\rho(G^o)$ is the power consumption of 
the origin graph.

If we set $diff_p$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the power consumption should never lower than the 90\% of origin one. Following is our implementation:

\begin{table}[!th]
\begin{tabular}{ll}
\hline
\textbf{Algorithm REAR : Phase One}\\
\hline
$\:\:$\textbf{Input:} $G(V, E)$, $threhold$;\\
$\:\:$\textbf{Output:} $S$ in which links should be switched off;\\
$\quad\qquad\quad$ $G(V, E-S)$ which is the final network topology;\\
$\:\:$1:\ \textbf{for} {each link $l$ in $E$}\\
$\:\:$2:\quad\ $\Gamma[l] \leftarrow u^e_l$;\\
$\:\:$3:\ Resort $\Gamma$ in increasing order based on $u^e_l$;\\
$\:\:$4:\ $S \leftarrow \emptyset$, $goon \leftarrow true$;\\
$\:\:$5:\ \textbf{while} {$goon$}\\
$\:\:$6:\quad\  $goon \leftarrow false$;\\
$\:\:$7:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
$\:\:$8:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)>threhold$\\
$\:\:$9:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
$\:\:$10:\quad\ \quad\ \quad\ $goon \leftarrow true$;\\
$\:\:$11:\quad\ \quad\ \quad\ \textbf{break};\\
$\:\:$12:\ \textbf{return} $S, G(V, E-S)$;\\
\hline
\end{tabular}
\end{table}

\subsection{Algorihtm Phase Two}
Once we get the output network topology from the first phase, it is time to compute
the robust routing. On one hand, computation process may cost too much time if we directly calculate the robust routing in 
the final graph; on the other hand, the robust routing based on the final graph may not be the best one.
There is a heuristic algorithm
based on the demand-oblivious routing on the origin graph, which should be obtained at first.
then adjust routing in details according to the links we switched off.

@@

\section{Samples and Proof}
For explaining OPRE clearly, we will show it in two simple topologies, Cliques and Cycles. With a specific power saving 
threshold, some links will be removed from the topology then robust routing will be computed. Taking two extreme examples from 
origin topology, one with no links removed, i.e the topology itself, and the other with no more link can be removed, i.e. 
spanning tree of the topology. And the corresponding thresholds are 0 and maximum value can be achieved. We prove the upper 
bound of OPRE for cycles and cliques in these two situations, and we say when taking a threshold between 0 and maximum value,
the corresponding OPRE is also bounded.

@@

\begin{lemma}
The upper bound of OPR for $C_n$ (the cycle on n vertices) and $K_n$ (the complete graph on n vertices) is 2-2/n.
\end{lemma}

Lemma 1 is proved in \cite{networking:oblivious} and it assumes all the links the same. We extend this lemma on $C_n$ and
$K_n$ with different capacity of links. In the latter proof, we use the extended $C_n$ and $K_n$ definition without specified.

\begin{theorem}
The upper bound of OPRE for spanning tree of $C_n$ is 1+$Max_{cap}$/$Min_{cap}$.
\end{theorem}

\begin{proof}
Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 2.(a) show the six
nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$. Now suppose a traffic in the 
topology then calculate the optimal routing for it, let $D_a$ and $C_a$ be the demand and capacity of the link $a$, 
without loss of generality, we say the link $d$ is the bottleneck, namely link with MLUR.

The spanning tree of $C_n$ is generated by removing one link from origin topology. There are two ways to generate 
the spanning tree, remove the link $d$ or remove the other link such as $f$.

For case \Rmnum{1}, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
is that all the traffic on the link $d$ will be put to the other path : $D \leftarrow C \leftarrow B \leftarrow A \leftarrow 
F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, we have OPRE in this routing situation:

@@

so we have OPRE in case \Rmnum{1} :

@@

For case \Rmnum{2}, similar to case \Rmnum{1}, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In case \Rmnum{2}.\Rmnum{1},
we have OPRE:

@@

Because the link utilization of link $d$ is the maximum one in origin topology, we have:

@@

So we get OPRE in case \Rmnum{2}.\Rmnum{1}:
\begin{equation}
    (1 + \frac{D_f}{D_d}) < \frac{C_d}{C_f} + 1
\end{equation}

In case \Rmnum{2}.\Rmnum{2}, we get OPRE:

@@

So we obtain OPRE:

@@

\begin{equation}
    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\} < 1 + \frac{Max_{cap}}{Min_{cap}}
\end{equation}

Particularly, if all the links have the same capacity, the upper bound equal to 2 for the spanning tree. Otherwise, the 
upper bound only dependent to the greatest ratio of link capacity.

\end{proof}

\begin{theorem}
The upper bound of OPRE for $C_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
\end{theorem}

\begin{proof}
The robust routing which will not trace demand on one link must be less optimal than the routing can trace demand on any link,
and obviously the former routing is one of the routing on the spanning tree of $C_n$. So the bound of Theorem 2 is also the 
bound of Theorem 3.

Particularly, If the links of $C_n$ have the same capacity, OPRE will reduce to OPR. According to Lemma 1, we have the inequality:

\begin{equation}
OPRE = OPR < 2 - \frac{2}{n} < 1 + \frac{Max_{cap}}{Min_{cap}} = 2
\end{equation}

\end{proof}

\begin{theorem}
The upper bound of OPRE for $K_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
\end{theorem}

\begin{proof}
Similar to the proof of Theorem 3, we say the robust routing which will not trace demand on one link must be less optimal than
the real optimal robust routing. And it is one routing of topology which remove one link from origin topology $K_n$. Without
loss of generality, we say the link $a$ is the bottleneck, and we will switch off it or other link like $b$, then consider
the OPRE when adjust the demand to other link.

In case \Rmnum{1}, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
traffic on link $a$. Otherwise if the link $b$ is the bottleneck, but we adjust the traffic on other links, it means that
we can do the same thing in the origin topology, and the bottleneck become link $b$ rather than $a$. It is conflict with our
assumption. So we have the OPRE as :

@@

In case \Rmnum{2}, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
the OPRE equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the OPRE:

@@

If the bottleneck become new link $c$, similar to our proof of circle topology, we can get OPRE:
\begin{equation}
    \frac{\frac{D_c + D_b}{C_c}}{\frac{D_a}{C_a}} = \frac{D_c * C_a}{D_a * C_c} + \frac{D_b * C_a}{D_a * C_c} < 1 + \frac{C_b}{C_c}
\end{equation}

So we obtain the same conclusion as circle topology, the OPRE must be :

\begin{equation}
    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\} = 1 + \frac{Max_{cap}}{Min_{cap}}
\end{equation}

When the links of $K_n$ is the same, Theorem 4 will reduce to Lemma 1. The upper bound is bounded.
\end{proof}

\begin{theorem}
The upper bound of OPRE for spanning tree of $K_n$ is $\frac{n^2}{2} Max_{cap}/Min_{cap}$.
\end{theorem}

\begin{proof}
Every link in the spanning tree will split the graph to two parts, the flow between two parts must need across this link,
Without loss of generality, let $l_{da}$ be the link with maximum link utilization. And let $l_{be}$ be the bottleneck link 
in the optimal routing for origin topology. So we have OPRE:

\begin{equation}
    \frac{\frac{\sum_{i,j \in V} D_{ij}}{C_{da}}}{\frac{D_{be}}{C_{be}}} = \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} 
\end{equation}

Because the $l_{be}$ is the bottleneck link, we have:

\begin{equation}
    \frac{D_{ij}}{C_{ij}} < \frac{D_{be}}{C_{be}}
\end{equation}

\begin{equation}
    \frac{D_{ij}}{D_{be}} < \frac{C_{ij}}{C_{be}}
\end{equation}

So we have OPRE:

\begin{equation}
    \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} < \sum_{i,j \in V} \frac{C_{ij}}{C_{be}}
\end{equation}

And we know that, the flow between two parts of topology must less than $\frac{n^2}{2}$, so OPRE must lower than:

\begin{equation}
    \sum_{i,j \in V} \frac{C_{ij}}{C_{be}} < \frac{n^2}{2} \frac{Max_{cap}}{Min_{cap}}
\end{equation}

\end{proof}

@@

When we switch off links, the topology lose connectivity and some routing paths will be failed, traffic on those paths will be 
adjusted to others, which result in the value of OPRE increased. We take margin from 1.5 to 3.5 and observe this phenomena from Figure.
Pay attention that we scale the y-axis as logarithm for comparing DMP and ERLU in one figure. Intuitively, we can see ERLU is always
better than DMP whatever margin or power saving target is, because ERLU consider much more than DMP, such as capacity and robust traffic 
flows. Another information from Figure 4 is that, we should carefully set the value of power saving for avoiding removing too much
links, which result in the OPRE increases rapidly, induce network congestions easily and make the robust routing be less `robust'.

@@

Comparing DMP and ERLU, the conclusion is similar to Figure 3, the latter is always better than the former. Even in some 
time, ERLU obtains more power saving but with a lower OPRE.

@@

We can observe that, ERLU is always shorter than DMP, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
equal to 1.5. And in the first removed links, the path stretching ratio is near 20\%.

@@

\bibitem{networking:gravity}
M.Roughan, A.Greenberg, C.Kalmanek, M.Rumsewicz, J.Yates, and Y.Zhang. Experience in measuring backbone traffic variability: models, metrics, measurements, and meaning. InProceedings of the 2nd Internet Measurement Workshop. ACM, 2002

\bibitem{networking:dmp}
A.P. Bianzino, L. Chiaraviglio, M. Mellia, Distributed algorithms for green IP networks, in: IEEE INFOCOM Workshop on Green Networking and Smart Grid, 2012

\end{thebibliography}
